Probability

### 2018-09-20 DATA606/Probability.Rmd
Updated Probability.Rmd
Additional work on the problem set

(a) Find the probability of drawing a hardcover book first then a paperback fiction book second when drawing without replacement.

(b) Determine the probability of drawing a fiction book first and then a hardcover book second, when drawing without replacement.

(c) Calculate the probability of the scenario in part (b), except this time complete the calculations under the scenario where the first book is placed back on the bookcase before randomly drawing the second book.

(d) The final answers to parts (b) and (c) are very similar. Explain why this is the case.

@@

@@

@@

(a) Describe the distribution of total personal income.

(b) What is the probability that a randomly chosen US resident makes less than $50,000 per year?

(c) What is the probability that a randomly chosen US resident makes less than $50,000 per year and is female? Note any assumptions you make.

(d) The same data source indicates that 71.8% of females make less than $50,000 per year. Use this value to determine whether or not the assumption you made in
part (c) is valid.

>>>>

(a) Find the probability of drawing a hardcover book first then a paperback fiction book second when drawing without replacement. **28/95 x 59/94 = 0.2947368 x 0.6276596 = 0.1849944**

(b) Determine the probability of drawing a fiction book first and then a hardcover book second, when drawing without replacement. **72/95 x 28/94 = 0.7578947 x 0.2978723 = 0.2257559**

(c) Calculate the probability of the scenario in part (b), except this time complete the calculations under the scenario where the first book is placed back on the bookcase before randomly drawing the second book.**72/95 x 28/95 = 0.7578947 x 0.2978723 = 0.2233795**

(d) The final answers to parts (b) and (c) are very similar. Explain why this is the case.  **Because they are basically the same scenario.  The only difference is the second one was drawing with replacement.**

@@

```{r}
fees <- c(rep(0, 54), rep(25, 34), rep(35+25, 12))
mean(fees)
```

**Average revenue = $15.70**

```{r}
sd(fees)
```
**Standard deviation = $20.05**

@@

```{r}
n <- 120
zero_fee <- n * .54
twenty_five_fee <- n * .34
sixty_fee <- n * .12
fees2 <-c(rep(0, zero_fee), rep(25, twenty_five_fee), rep(60, sixty_fee))
mean(fees2)
sd(fees2)
```

**The average is $15.59 with a standard deviation of $19.98.  This assumes that the proportions hold, that the airplane has space for the 70 bags and that the airline prices are unchanged.  I think that these are all reasonable assumptions.**

@@

(a) Describe the distribution of total personal income. **Long tailed/right skewed**

(b) What is the probability that a randomly chosen US resident makes less than $50,000 per year? **0.02 + 0.047 + 0.158 + 0.183 + 0.213 = 0.621**

(c) What is the probability that a randomly chosen US resident makes less than $50,000 per year and is female? Note any assumptions you make.  **0.41 the same as the probability that they are female.  This assumes income is not dependant on gender (a horrible assumption which I don't believe is true).**

(d) The same data source indicates that 71.8% of females make less than $50,000 per year. Use this value to determine whether or not the assumption you made in
part (c) is valid.  **This indicates that the assumption of income level is independant of gender is not true.**
